---
title: "local sensitivity analysis with mrgsolve"
output: github_document
---

```{r,setup,include=FALSE}
knitr::opts_chunk$set(
  comment = '.', message=FALSE, warning = FALSE, 
  fig.path = "man/images/readme-"
)
```

# Model
Load the vera package and a model from the mrgsolve package.  We 
increase the tolerance a bit as well as the maximum step size.
```{r,message=FALSE}
library(vera)

mod <- modlib(
  "pbpk", 
  end = 12, delta = 0.1, 
  atol = 1E-20, rtol = 1E-12, hmax=0.5
)
```

# Scenario
Create a function that uses the model to simulate a certain scenario.  For now, 
we just simulate a single dose.
```{r}
fun <- function(p,dose) {
  mod %>% 
    param(p) %>% 
    ev(dose) %>% 
    mrgsim_df()
}

d <- ev(amt = 100)
```

# Sensitivity analysis

Use `vera::lsa()`.  We pick the paramters that we want to fiddle with (`par`)
and the output that we want to look at (`Cp` and `Amu` - the amount in the 
muscle compartment).  `d` gets passed through to the function as `dose`. 
```{r}
out <- lsa(mod, fun, par = "Kpli,Kpmu,BW,Ka", var = "Cp,Amu", dose = d)
```

# Ouput

The output is long and ready to send in to `ggplot2`.  
```{r}
head(out)
```

There is a default plotting method as well.

```{r}
plot(out)
```


