---
title: "local sensitivity analysis with mrgsolve"
output: github_document
---

```{r,setup,include=FALSE}
knitr::opts_chunk$set(
  comment = '.', message=FALSE, warning = FALSE, 
  fig.path = "man/images/readme-"
)
```

# Model
Load the vera package and a PBPK model from the mrgsolve package.  We 
decrease the tolerance a bit as well as the maximum step size.
```{r,message=FALSE}
library(vera)

mod <- modlib(
  "pbpk", 
  end = 12,     delta = 0.1, 
  atol = 1E-20, rtol  = 1E-12, hmax = 0.5
)
```

# Scenario
Create a function that uses the model to simulate a certain scenario.  For now, 
we just simulate a single dose.
```{r}
fun <- function(p,dose) {
  mod %>% 
    param(p) %>% 
    ev(dose) %>% 
    mrgsim()
}

d <- ev(amt = 100)

fun(param(mod),d) %>% plot(Cp+Amu~time)
```

# Sensitivity analysis

Use `vera::lsa()`.  We pick the __parameters__ that we want to fiddle with 
(`par`):

- `Kpli` liver partition coefficient
- `Kpmu` muscle partition coefficient
- `Kpad` adipose tissue partition coefficient
- `BW` body weight 

Also specify the __output__ that we want to look at (`var`):

- `Cp` - venous concentration
- `Amu` - amount in the muscle compartment

`d` gets passed through to the function as `dose`. 

```{r}
out <- lsa(mod, fun, par = "Kpli,Kpmu,Kpad,BW", var = "Cp,Amu", dose = d)
```

# Ouput

The output is long and ready to send in to `ggplot2`.  
```{r}
head(out)
```

There is a default plotting method as well.

```{r}
plot(out)
```


